% Modern Single-Column Resume Template
% Design Philosophy: Clean, ATS-friendly layout with professional navy accents
% Font: Lato for modern, readable appearance
% Spacing: Generous white space for better readability and visual hierarchy

\documentclass[11pt,a4paper]{article}

% ============= PACKAGES =============
% inputenc is unnecessary on UTF-8 engines (XeLaTeX/LuaLaTeX)
% \usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lato} % Modern, professional sans-serif font
\usepackage[hidelinks]{hyperref} % Clean hyperlinks without colored boxes
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage[final]{microtype} % Better kerning & fewer broken ligatures

% Encoding & hyphenation safety for ATS/PDF export
\hyphenpenalty=10000
\exhyphenpenalty=10000
\tolerance=1000
\emergencystretch=3em

% ============= PAGE LAYOUT =============
% Optimized margins for single-column layout - balanced white space
\geometry{
  top=0.3in,
  bottom=0.5in,
  left=0.65in,
  right=0.65in,
  nofoot
}

% ============= COLOR SCHEME =============
% Professional navy palette - subtle yet distinctive
\definecolor{navyblue}{RGB}{25, 55, 100}      % Primary: Section headers
\definecolor{darkgray}{RGB}{60, 60, 60}       % Body text
\definecolor{lightgray}{RGB}{120, 120, 120}   % Secondary text

% ============= SECTION FORMATTING =============
% Navy-colored section headers with subtle underline for visual separation
\titleformat{\section}
  {\color{navyblue}\Large\bfseries\raggedright}
  {}{0em}
  {}
  [\color{navyblue}\titlerule]

\titlespacing*{\section}{0pt}{10pt}{4pt}

% ============= LIST FORMATTING =============
% Compact bullets with optimal spacing for content density
\setlist[itemize]{
  leftmargin=*,
  itemsep=1pt,
  topsep=3pt,
  parsep=0pt,
  partopsep=0pt,
  label=\textbullet
}

% ============= CUSTOM COMMANDS =============
% Consistent formatting for job titles and dates with proper alignment
\newcommand{\resumeheading}[4]{
  \noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{\color{navyblue}#1} & \textit{\color{lightgray}#2} \\
    \textit{#3} & \textit{\color{lightgray}#4}
  \end{tabularx}\vspace{1pt}
}

% Project headings with tech stack emphasis
\newcommand{\projectheading}[2]{
  \textbf{\color{navyblue}#1} \hfill \textit{\color{lightgray}#2}
  \vspace{-2pt}
}

% Skill category formatting for clean organization with consistent wrapping
\newcommand{\skillcategory}[2]{
  \textbf{\color{navyblue}#1:} \raggedright #2
}

% ============= DOCUMENT START =============
\begin{document}
\pagestyle{empty} % Clean layout without page numbers

% ============= HEADER SECTION =============
% Centered name with contact info - optimized for ATS parsing
\begin{center}
  {\Huge\bfseries\color{navyblue}RAMITH K S} \\[4pt]
  {\Large\color{darkgray}Senior Backend Engineer} \\[8pt]
  \color{darkgray}
  \href{tel:+919481968808}{+91 9481968808} $|$ 
  \href{mailto:ramithgowdakundoor123@gmail.com}{ramithgowdakundoor123@gmail.com} $|$ 
  \href{https://www.linkedin.com/in/ramith-k-s}{LinkedIn: ramith-k-s} $|$ 
  \href{https://github.com/ramithks}{GitHub: ramithks}
\end{center}

% ============= PROFESSIONAL SUMMARY =============
\section{Professional Summary}
\color{darkgray}
{\small Senior Backend Engineer with 5+ years of experience building scalable Python/FastAPI services, distributed systems and cloud-native applications. Experienced in developing AI-enabled backend features using LangChain, LLM APIs, RAG pipelines and lightweight machine-learning models.}

% ============= PROFESSIONAL EXPERIENCE =============
\section{Professional Experience}
\resumeheading{Thermo Fisher Scientific}{February 2026 -- Present}{Senior Backend Engineer}{Bengaluru}
\vspace{2pt}
\textit{\small Tech Stack: Python, FastAPI, Kubernetes, Kafka, Grafana, Microservices}
\vspace{2pt}
\begin{itemize}
\item Build Python/FastAPI services for high-reliability e-commerce checkout and order-processing workflows on Kubernetes.
\item Implemented Kafka-based acknowledgement processing, validation and status updates across asynchronous order workflows.
\item Improved reliability through structured error handling, retries, observability and integration testing.
\end{itemize}

\vspace{3pt}

\resumeheading{Zolnoi Innovations}{October 2024 -- Present}{Backend Engineer}{Bengaluru}
\vspace{2pt}
\textit{\small Tech Stack: FastAPI, PostgreSQL, Redis, MongoDB, APScheduler, Docker, AWS}
\vspace{2pt}
\begin{itemize}
\item Built industrial IoT analytics APIs using FastAPI, PostgreSQL, Redis and MongoDB, processing 10,000+ daily requests.
\item Integrated rule-based and ML-generated anomaly insights into production, energy and cycle-time analytics workflows.
\item Designed a multi-channel alerting system with retries and failure handling, processing 5,000+ notifications daily.
\end{itemize}

\vspace{3pt}

\resumeheading{JustPoll (Streetlab Internet Pvt Ltd)}{July 2021 -- August 2024}{Founder \& CTO}{Bengaluru}
\vspace{1pt}
\textit{\small Tech Stack: Node.js, TypeScript, PostgreSQL, Redis, AWS (ECS, S3), Docker, Grafana}
\vspace{2pt}
\begin{itemize}
\item Founded and scaled a social platform to 1,500+ Android and 600+ iOS users; architected TypeScript backend and Flutter app.
\item Boosted query performance by 40\% via schema optimization; cut deployment time by 60\% with ECS autoscaling and CI/CD pipelines.
\item Led 5-member engineering team through 20+ production releases; improved user retention by 65\% through mentoring and architecture reviews.
\end{itemize}

\vspace{2pt}

% ============= TECHNICAL SKILLS =============
\section{Technical Skills}

\skillcategory{Backend \& Languages}{Python, FastAPI, AsyncIO, REST APIs, Node.js, TypeScript}

\vspace{2pt}

\skillcategory{Generative AI \& Machine Learning}{LangChain, LangGraph, LLM API Integration, RAG, Prompt Engineering, Structured Outputs, Embeddings, scikit-learn, Model Serving}

\vspace{2pt}

\skillcategory{AI Data \& Storage}{pgvector, Vector Search, PostgreSQL, Redis, MongoDB, Pandas, NumPy}

\vspace{2pt}

\skillcategory{Systems \& Cloud}{Microservices, Kafka, Event-Driven Architecture, Kubernetes, Docker, AWS, GitHub Actions, CI/CD, Observability}

\vspace{2pt}

\skillcategory{Testing \& Reliability}{Pytest, Integration Testing, Retry and Fallback Workflows, Root Cause Analysis}

\vspace{2pt}

\skillcategory{Additional}{React, Flutter}

\vspace{2pt}

% ============= EDUCATION =============
\section{Education}

\textbf{\color{navyblue}Bachelor of Computer Applications} \hfill \textit{\color{lightgray}2018 -- 2021}\\
Christ University, Bangalore \hfill CGPA: 3.3/4.0

\vspace{2pt}

% ============= RECOGNITION =============
\section{Recognition}

\begin{itemize}
\item HackBangalore Winner 2024
\item AWS Cloud Foundations Certified
\item Open Source Contributor
\end{itemize}

\vspace{2pt}

% ============= KEY PROJECTS =============
\section{Key Projects}

\projectheading{AlgoHabit | AI-Powered Learning Platform}{\href{https://algohabit.com}{algohabit.com} | 50+ Active Users}
\vspace{1pt}
\textit{\small Tech Stack: React, TypeScript, LangChain, RAG, pgvector, OpenRouter AI, Supabase, PWA}
\vspace{2pt}
\begin{itemize}
\item Built and launched AlgoHabit, an AI-powered DSA learning platform designed around habit formation, streaks, and gamified progression.
\item Built a LangChain-based LLM pipeline using OpenRouter, prompt templates, structured output parsing, retries and model fallback to generate personalised learning plans.
\item Implemented a RAG pipeline using document chunking, embeddings and pgvector-based semantic search to generate syllabus-grounded learning recommendations.
\item Engineered React PWA achieving 95+ Lighthouse performance score with offline-first architecture.
\end{itemize}

\vspace{7pt}

\projectheading{Ledgerly | Smart Finance Tracker SaaS}{Personal Project}
\vspace{1pt}
\textit{\small Tech Stack: FastAPI, React, PostgreSQL, scikit-learn, MLflow, Pytest}
\vspace{2pt}
\begin{itemize}
\item Built scikit-learn pipelines using TF-IDF and Logistic Regression for transaction classification, statistical forecasting for spending trends and MAD-based anomaly detection.
\item Served ML predictions through FastAPI endpoints with Pydantic validation, model loading, logging and health checks.
\item Used MLflow for basic experiment tracking, model metrics and version comparison.
\end{itemize}

\vspace{7pt}

\projectheading{AG-WALLET | Agricultural Supply Chain Platform}{Android Application}
\vspace{1pt}
\textit{\small Tech Stack: Android (Java), MySQL, Google Maps API}
\vspace{2pt}
\begin{itemize}
\item Built Android app connecting farmers, distributors, and customers for transparent pricing and direct market access.
\item Implemented real-time price monitoring enabling farmers to track distributor pricing and maximize profit margins.
\item Integrated Google Maps API for location-based distributor discovery and rating system for quality-based selection.
\end{itemize}

\vspace{7pt}

\projectheading{HelpMyBuddy | HackBangalore Winner 2024}{\href{https://github.com/SiliconNinjas/HelpMyBuddy}{GitHub Link}}
\vspace{2pt}
\begin{itemize}
\item Developed React Native prototype connecting homeowners with service providers via geolocation matching within 5km.
\item Built Node.js backend with booking system and real-time availability tracking.
\end{itemize}

\end{document}